---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
#rm(list = ls())

# data load
data_1976_2016 <- read.csv("/Users/junjiexie/Documents/gu校内生活/501/Assignment1/1976-2020president/1976-2020-president.csv")
data_2016 <- read.csv("/Users/junjiexie/Documents/gu校内生活/501/Assignment1/2016president/2016-precinct-president.csv")
```


```{r}
# have a quick look of two dataset and subset dataset
str(data_1976_2016)
```
```{r}
str(data_2016)
```
```{r}
# select the necessary subset of the whole data set

data_1976_2016_need <- subset(data_1976_2016, select = c("year", "state", "candidate", "party_simplified", "candidatevotes", "totalvotes"))
data_2016_need <- subset(data_2016, select = c("year", "state", "candidate", "party", "votes"))


# fix the type of the dataset
# data_1976_2016_need$party_simplified <- lapply(data_1976_2016_need$party_simplified, as.factor)
# data_2016_need$party <- lapply(data_2016_need$party, as.factor)

```
```{r}
# check if there is duplicate rows in the dataset
duplicated(data_1976_2016_need) %>%
    sum()
duplicated(data_2016_need) %>%
  sum()
```

```{r}
library(tidyverse) 
# library(scrubr)

# remove the duplicate of data_2016_need
data_2016_need <- distinct(data_2016_need)

```

```{r}
# check the missing value of the data_1976_2016_need
for(i in colnames(data_1976_2016_need)) {
  print(paste("data_1976_2016_need, the nubmer of missing value of", i,"is",sum(is.na(data_1976_2016_need$i))))
}

print("-------------------------------")

# check the missing value of data_2016_need
for(i in colnames(data_2016_need)) {
  print(paste("data_2016_need, the nubmer of missing value of", i,"is",sum(is.na(data_2016_need$i))))
}

# the data is so clean that I can't not find a missing value of it
```
```{r}
# check the outlier of the dataset

library(outliers)
library(ggplot2)

# data_1976_2016
ggplot(data_1976_2016_need, aes(x = 1:length(candidatevotes), y = candidatevotes)) +
    geom_point()

 # base on the normal distribution assumption
outlier_scores_1976_2016 <- scores(data_1976_2016_need$candidatevotes)
outlier_scores_1976_2016_1 <- scores(data_1976_2016_need$totalvotes)
data_1976_2016_need <- data_1976_2016_need[outlier_scores_1976_2016 > 3| outlier_scores_1976_2016 < -3, ]
data_1976_2016_need <- data_1976_2016_need[outlier_scores_1976_2016_1 > 3| outlier_scores_1976_2016_1 < -3, ]

# data_2016
outlier_scores_2016 <- scores(data_2016_need$votes)
data_2016_need <- data_2016_need[outlier_scores_2016 > 3 | outlier_scores_2016 < -3, ]
```

```{r}
#typeof(data_1976_2016_need$party_simplified)
#typeof(data_2016_need$party)

#data_1976_2016_need$party_simplified <- lapply(data_1976_2016_need$party_simplified, unlist)
#data_2016_need$party <- lapply(data_2016_need$party, unlist)
```

```{r}
# output clean data
write.csv(data_1976_2016_need,file="data_1976_2016_clean.csv")
write.csv(data_2016_need,file="data_2016_clean.csv")
```


Find the dataset description from the website.

U.S. President Returns 1976–2016

The data file `1976-2016-president` contains constituency (state-level) returns for elections to the U.S. presidency from 1976 to 2016.  The data source is the document "[Statistics of the Congressional Election](http://history.house.gov/Institution/Election-Statistics/Election-Statistics/)," published biennially by the Clerk of the U.S. House of Representatives.

## Variables
The variables are listed as they appear in the data file.

### year
 - **Description**: year in which election was held

---------------

### office
  - **Description**: U.S. PRESIDENT

---------------

### state
 - **Description**: state name

 ---------------

### state_po
 - **Description**: U.S. postal code state abbreviation

 ---------------

### state_fips
 - **Description**: State FIPS code

----------------

### state_cen
 - **Description**: U.S. Census state code

 ---------------

### state_ic
 - **Description**: ICPSR state code

 ---------------

### candidate
  - **Description**: name of the candidate
  - **Note**: The name is as it appears in the House Clerk report.

----------------

### party_detailed
- **Description**: party of the candidate (always entirely uppercase)
- **Note**: Parties are as they appear in the House Clerk report. In states that allow candidates to appear on multiple party lines, separate vote totals are indicated for each party.  Therefore, for analysis that involves candidate totals, it will be necessary to aggregate across all party lines within a district.  For analysis that focuses on two-party vote totals, it will be necessary to account for major party candidates who receive votes under multiple party labels. Minnesota party labels are given as they appear on the Minnesota ballots. Future versions of this file will include codes for candidates who are endorsed by major parties, regardless of the party label under which they receive votes.

### party_simplified
- **Description**: party of the candidate (always entirely uppercase)
The entries will be one of: DEMOCRAT, REPUBLICAN, LIBERTARIAN, OTHER

----------------

### writein
- **Description**: vote totals associated with write-in candidates
- Coding:

|:--|:--|
| "TRUE" | write-in candidates |
| "FALSE" | non-write-in candidates |

----------------

### candidatevotes
  - **Description**: votes received by this candidate for this particular party
- **Note**: Massachusetts and New York returns often contains entries for "blank," "other/blank," "scattering/blank," and the like.  For analyses that depend on an accurate count of votes cast for candidates (rather than turnout, including blank ballots), consult state returns.  Future versions of this dataset will distinguish blank ballots from votes cast for scattering candidates.

----------------

### totalvotes
 - **Description**: total number of votes cast for this election

-----------------------------------------------------------------------------
U.S. President Precinct-Level Returns 2016


This codebook describes a dataset on precinct-level returns for elections to
the U.S. presidency.

Each record in the dataset gives the number of votes reported from a precinct
for a candidate.

### year

Year of election.


### state

State name.


### state_postal

State U.S. Postal Service abbreviation (two-letter ISO 1366 code).


### state_fips

Numeric state FIPS 5-2 code.


### state_icpsr

Numeric ICPSR state code.


### county_name

County name.

Source: Census Bureau [National Counties Gazetteer
File](https://www.census.gov/geo/maps-data/data/gazetteer2017.html).


### county_ansi

County ANSI code.

Source: Census Bureau [National Counties Gazetteer
File](https://www.census.gov/geo/maps-data/data/gazetteer2017.html).


### county_fips

Numeric FIPS 6-4 code, the concatenation of two-digit `state_fips` and three-
digit county FIPS codes.

Source: Census Bureau [National Counties Gazetteer
File](https://www.census.gov/geo/maps-data/data/gazetteer2017.html).


### county_lat

County latitude (decimal degrees).

Source: Census Bureau [National Counties Gazetteer
File](https://www.census.gov/geo/maps-data/data/gazetteer2017.html).


### county_long

County longitude (decimal degrees).

Source: Census Bureau [National Counties Gazetteer
File](https://www.census.gov/geo/maps-data/data/gazetteer2017.html).


### jurisdiction

The name of the administrative jurisdiction, typically a county, as it appeared
in source data.

Source: Precinct returns for `jurisdiction`.


### precinct

The name of the precinct, as it appeared in source data.

Source: Precinct returns for `jurisdiction`.


### office

The office for which the `candidate` ran.

Source: Precinct returns for `jurisdiction`.


### district

District associated with the `office`, where applicable.

Source: Precinct returns for `jurisdiction`.


### stage

The electoral stage, either `gen` for general elections or `pri` for primary
elections.


### special

Whether the election was a special election, either `TRUE` for special
elections or `FALSE` otherwise.

Source: Precinct returns for `jurisdiction`.


### candidate

The name of the candidate.

Candidate names are standardized across jurisdictions.

Source: Precinct returns for `jurisdiction`.


### candidate_last

Candidate's last name.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_first

Candidate's first name.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_middle

Candidate's middle name.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_normalized

A normalizing transformation of the candidate's name for joins by name. This is
a single word from `candidate`, usually the last name, in lowercase. In the
case of hyphenated names, only the final name is included.

Source: MEDSL.


### candidate_full

Candidate's official full name.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_suffix

Candidate name suffix.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_nickname

Candidate's nickname.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_fec

Candidate's [FEC
identifier](https://www.fec.gov/data/advanced/?tab=candidates). Multiple FEC
IDs appear concatenated, separated by a semicolon and space (`; `).

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project and [FEC](https://www.fec.gov/data/advanced/?tab=candidates).


### candidate_fec_name

Candidate's name as it appears in FEC data.

Source: [FEC](https://www.fec.gov/data).


### candidate_google

Candidate's [Google Knowledge Graph](https://developers.google.com/knowledge-
graph) entity identifier.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_govtrack

Candidate's [GovTrack.us](https://www.govtrack.us) identifier.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_icpsr

Candidate's [ICPSR](https://www.icpsr.umich.edu) identifier.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_maplight

Candidate's [MapLight](https://maplight.org) identifier.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_opensecrets

Candidate's [OpenSecrets.org](https://www.opensecrets.org) identifier.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_wikidata

Candidate's [WikiData](https://www.wikidata.org) identifier.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### candidate_party

Candidate's party affiliation. Values may differ from `party`, which gives the
candidate's party on the ballot.

Source: The [@unitedstates](https://github.com/unitedstates/congress-legislators)
project.


### writein

Whether the record describes a write-in candidate, either `TRUE` or `FALSE`.

Source: Precinct returns for `jurisdiction`.


### party

Party of the `candidate`, where applicable. Candidates may run on multiple
party lines, so to compute two-party vote shares or candidate vote totals,
aggregate over `party`.

Party names are standardized across jurisdictions.

Source: Precinct returns for `jurisdiction`.


### mode

Vote mode, e.g., `mail` or `Election Day`.

Source: Precinct returns for `jurisdiction`.


### votes

Number of votes received.

Source: Precinct returns for `jurisdiction`.