---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".
```{r}
library(tidyverse)
library(fpc) 
library(ggplot2)
# install.packages("fpc")
# install.packages("wordcloud")
# install.packages("tm")
# install.packages("Snowball")
```
The code chunk appears:
```{r}
#prepare for the dataset
c1 <- c(2,7,10,15,10,35,67,51,29)
c2 <- c(2,8,10,12,25,32,67,89,91)
c3 <- c(3,25,37,46,13,25,99,76,51)
dataset <- data.frame(first=c1,second=c2,third=c3)
```

Type any R code in the chunk, for example:
```{r}
#show the boxplot of three attribute
dataset %>%
  gather(Attributes, values) %>%
  ggplot(aes(x=reorder(Attributes, values, FUN=median), y=values, fill=Attributes)) +
  geom_boxplot(show.legend=FALSE) +
  labs(title="Dataset Attributes - Boxplots") +
  theme_bw() +
  theme(axis.title.y=element_blank(),
        axis.title.x=element_blank()) +
  ylim(0, 30) +
  coord_flip()
```
```{r}
# Normalization
Norm <- as.data.frame(scale(dataset))
```
```{r}
# Now cluster
set.seed(1234)
cluster_data <- kmeans(Norm, centers=2)
```
```{r}
# Show cluster label
cluster_data$cluster
```
```{r}
# show cluster center,it's already normalized
cluster_data$centers
```
```{r}
# use silhouette coefficient to find the best k
storage <- c()
for (i in 2:5){
  result <- kmeans(Norm,i)
  stats <- cluster.stats(dist(Norm), result$cluster)
  storage <- append(storage,stats$avg.silwidth)
}
```


```{r}
# we find that k=2 the ilhouette coefficient is the best (0.59)
print(storage)
```


```{r}
# now show the picture of k=2，scatter and density picture
ggpairs(cbind(dataset, Cluster=as.factor(cluster_data$cluster)),
        columns=1:3, aes(colour=Cluster, alpha=0.5),
        lower=list(continuous="points"),
        upper=list(continuous="blank"),
        axisLabels="none", switch="both") +
        theme_bw()

```
Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
